---
title: "Intensity norming"
author: "Will Clapp"
date: "3/1/2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
```



```{r cars}
df.norming_data <- read.csv("/Users/willclapp/Desktop/QP1/QP1_Experiments/Exp_3/intensity_norming/intensity_norming-sandbox-trials.csv")
```


Filter out the test runs

```{r pressure, echo=FALSE}
df.norming_data <- df.norming_data %>% 
  filter(workerid > 3)
```


Filter out instruction pages and audio trials

```{r}

df.norming_data <- df.norming_data %>% 
  filter(test_part=="sine" | test_part=="syll")

```

Drop extraneous info

```{r}
df.norming_data <- df.norming_data %>% 
  select(-c(proliferate.condition, internal_node_id, button_pressed, stimulus, error))

```

Add a column to interpret key press

```{r}
df.norming_data <-df.norming_data %>% 
  mutate(response = ifelse(key_press==32, "SAME", ifelse(key_press==83, "FIRST", "SECOND")))


```


Now break into sine and syllables

```{r}
df.sine <- df.norming_data %>% 
  filter(test_part=="sine")

df.syll <- df.norming_data %>% 
  filter(test_part=="syll")

```



___________________________________________________________________________________________________________________________________________
SINE --- SINE --- SINE --- SINE --- SINE --- SINE --- SINE --- SINE --- SINE --- SINE --- SINE --- SINE --- SINE --- SINE --- SINE --- SINE 
___________________________________________________________________________________________________________________________________________

```{r}
df.sine <- df.sine %>% 
  mutate(winner=NA) %>% 
  mutate(loser=NA)

for (row in nrow(df.sine)) {
  df.sine$winner = ifelse(df.sine$response=="SAME", "neither", ifelse(df.sine$response=="FIRST", df.sine$first_sound, df.sine$second_sound))
}

for (row in nrow(df.sine)) {
  df.sine$loser = ifelse(df.sine$response=="SAME", "neither", ifelse(df.sine$response=="FIRST", df.sine$second_sound, df.sine$first_sound))
}


df.sine_winners <- df.sine %>% 
  group_by(winner) %>% 
  tally()

df.sine_losers <- df.sine %>% 
  group_by(loser) %>% 
  tally()
```
Need to make it a little less steep
___________________________________________________________________________________________________________________________________________
SYLL --- SYLL --- SYLL --- SYLL --- SYLL --- SYLL --- SYLL --- SYLL --- SYLL --- SYLL --- SYLL --- SYLL --- SYLL --- SYLL --- SYLL --- SYLL 
___________________________________________________________________________________________________________________________________________



```{r}
df.syll <- df.syll %>% 
  mutate(winner=NA) %>% 
  mutate(loser=NA)

for (row in nrow(df.syll)) {
  df.syll$winner = ifelse(df.syll$response=="SAME", "neither", ifelse(df.syll$response=="FIRST", df.syll$first_sound, df.syll$second_sound))
}

df.syll_winners <- df.syll %>% 
  group_by(winner) %>% 
  tally()

for (row in nrow(df.syll)) {
  df.syll$loser = ifelse(df.syll$response=="SAME", "neither", ifelse(df.syll$response=="FIRST", df.syll$second_sound, df.syll$first_sound))
}

df.syll_losers <- df.syll %>% 
  group_by(loser) %>% 
  tally()

```



Then furthe split based on comparison type

```{r}
df.cross <- df.syll %>% 
  filter(type=="cross_continuum_voiced" | type=="cross_continuum_voiceless")

df.cross_winners <- df.cross %>% 
  group_by(winner) %>% 
  tally()

df.cross_losers <- df.cross %>% 
  group_by(loser) %>% 
  tally()

df.internal <- df.syll %>% 
  filter(type=="continuum_internal")

df.internal_winners <- df.internal %>% 
  group_by(winner) %>% 
  tally()

df.internal_losers <- df.cross %>% 
  group_by(loser) %>% 
  tally()



```
SO these are really pretty consistent within continua
Need to drag the AH down a bit and the AA up















